\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-03-20 paper/main.tex
Added tool availability from Intro to a new section

\Fix{Add a "Tool availablity" section and move the details there, upload the video to YouTube, archive 
the tool at zenodo}

We present \tname, a database of curated reproducible bugs to
enable credible evaluation of DL library testing techniques. \tname\ is
equipped with a command-line interface to enable researchers to analyze
and reproduce bug instances. The following screencast demonstrates some
of the features of \tname:

\url{https://tinyurl.com/BugsInDLLs}\\

\tname\ has been under active development since March 21, 2024, the
day of the first commit in its GitHub repository. Two UROP students,
two PhD students, and two faculty were involved in the work during
this period. \tname\ is publicly available from the following URL:

\url{https://github.com/ncsu-swat/bugsindlls}

@@

>>>>

% \Fix{Add a "Tool availablity" section and move the details there, upload the video to YouTube, archive 
% the tool at zenodo}

We present \tname, a database of curated reproducible bugs to
enable credible evaluation of DL library testing techniques. \tname\ is
equipped with a command-line interface to enable researchers to analyze
and reproduce bug instances.

\tname\ has been under active development since March 21, 2024, the
day of the first commit in its GitHub repository. Two UROP students,
two PhD students, and two faculty were involved in the work during
this period. Details on tool availability is provided in
Section~\ref{sec:tool-availability}.

@@

\section{Tool Availability}
\label{sec:tool-availability}
\tname\ is publicly available from the following URL:

\url{https://github.com/ncsu-swat/bugsindlls}\\

The following screencast demonstrates some
of the features of \tname:

\url{https://tinyurl.com/BugsInDLLs}\\
\Fix{Upload to YouTube with voiceover and add link here, archive 
the tool at zenodo}
